
---
title: "FastMapping report"
params:
  input: NA
  output: NA
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: tibble
  word_document:
    toc: yes
    toc_depth: '2'
editor_options: 
  chunk_output_type: console
---

```{r, setup, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(ggplot2)

options(knitr.table.format = function() {
  if (knitr::is_latex_output()) 
  "latex" else "pandoc"
})

knitr::opts_chunk$set(echo = FALSE)

#        ##Data statistics
# DescrStatistics <- function (DataF) {
#   NumberOfData<-length(DataF)
#   Median <- median(DataF,  na.rm = TRUE)
#   Mean <- mean(DataF, na.rm = TRUE) 
#   Minim <- min(DataF, na.rm = TRUE) 
#   Maxim <- max(DataF, na.rm = TRUE) 
#   StDev <- sd(DataF, na.rm = TRUE)
#   DescrSt<-round(c("Number of data points" = NumberOfData,
#              "Median" = Median,
#              "Mean" = Mean,
#              "Minimum" = Minim,
#              "Maximum" = Maxim,
#              "Standard deviation" = StDev),2)
#   return(DescrSt) }
# TablaResumen<-cbind(
#   #Raw Data Statistics
#   "Raw Data" = DescrStatistics(DatosProcedimientoOriginales[,3] ),
#   #Filtered data
#   "Filtered data" = DescrStatistics(DatosUtilizadosProcedSinOutliers_Inlierns[,3])
# )
# table(addNA(CondicFinal[,4]))


myChoice <- list(Exponential ="Exp",
                 Shperical = "Sph",
                 Gaussian = "Gau",
                 Matern = "Mat",
                 "M. Stein's" ="Ste",
                 Circular = "Cir",
                 Linear = "Lin",
                 Power = "Pow",
                 Wave = "Wav",
                 Pentaspherical = "Pen",
                 Hole = "Hol")

Coordenadas <- c(params$input$xmapa,params$input$ymapa)
VariablesTarget <- params$input$rto

```


```{r}
if (identical(rmarkdown::metadata$runtime, "shiny"))
  shiny::setProgress(0.25)  # set progress to 25%
```




```{r, eval = FALSE}
# params
# 
# 
# structure(params)
```


`r if(!is.null(params$output$Tabla)){"# Summary of Data"}`

`r if(!is.null(params$output$Tabla)) {ifelse(!is.null(params$output$DataDep),"Summary of data before depuration","Summary of data")}`

```{r, eval=!is.null(params$output$Tabla)}
#Si existe la tabla 
TablaOriginal <- params$output$Tabla
Coordenadas <- c(params$input$xmapa,params$input$ymapa)
VariablesTarget <- params$input$rto

kable(summary(TablaOriginal[VariablesTarget]))

if(length(VariablesTarget)==1){
  ggplot(TablaOriginal) +
    geom_boxplot(data = TablaOriginal, aes_string(y = VariablesTarget),  fill="#FFBF00") +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
}

```


`r if(!is.null(params$output$DataDep)){"Summary of data after depuration"}`

```{r, eval=!is.null(params$output$DataDep)}

#Si existe la tabla depurada
TablaOriginalDep <- params$output$DataDep

TablaOriginalDep <- TablaOriginalDep[TablaOriginalDep$Condition=="NormalPoint",]

kable(summary(TablaOriginalDep[VariablesTarget]))
try(
  if(length(VariablesTarget)==1) {
    
      ggplot(TablaOriginalDep) +
    geom_boxplot(aes_string(y = VariablesTarget),  fill="#FFA700") +
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
    
  }
)

```



```{r, eval= !is.null(params$output$DataDep) && !is.null(params$output$Tabla)}
BothData <- rbind(
  data.frame("myData" = "Raw data", "myValues" = TablaOriginal[[VariablesTarget]]),
  data.frame("myData" = "Depurated data", "myValues" = TablaOriginalDep[[VariablesTarget]]))
ggplot(BothData) +
  geom_boxplot(aes(y = myValues, x = myData),  fill="#FFA700") +
  labs(x = "Condition", y = VariablesTarget)
```



```{r}
if (identical(rmarkdown::metadata$runtime, "shiny"))
  shiny::setProgress(0.50)  # set progress to 50%
```

`r if(sum(!do.call(rbind, lapply(params$output, is.null)))==1) {"You did not execute a procedure"}`

`r if(!is.null(params$output$MiKrige)) {"## Interpolation cross-validation results"}`

```{r, eval=!is.null(params$output$MiKrige), results='asis'}
# names(params$output)

if(length(params$output$SelectedMdls)>1) {
  cat(paste(names(myChoice[myChoice %in% params$output$SelectedMdls ]), collapse = ", "),"models were adjusted. \n\n\n")
} else {
  cat(names(myChoice[myChoice %in% params$output$SelectedMdls ]),"model were adjusted. \n\n\n")
}

kable(params$output$MiKrige[ , sapply(params$output$MiKrige, function(x) !all(is.na(x))) ])


plot(params$output$Variograma)
print(params$output$variogg)
#   # ValoresOutput <- reactiveValues(Tabla=NULL, TablaCoordTrans=NULL,DataDep=NULL,NombresCol=NULL,
#   #                                 SelectedMdls=NULL,  MiKrige=NULL,
#   #                                 Variograma=NULL, Mygr=NULL, kriging=NULL, GeoTiff=NULL,
#   #                                 Clasificacion=NULL, GraficoConglom=NULL)
# # browser()

if(!is.null(params$output$kriging)) plot(params$output$kriging)
# if(!is.null(params$output$GeoTiff)) plot(params$output$GeoTiff)
# if(!is.null(params$output$Clasificacion)) plot(params$output$Clasificacion)
```



`r if(!is.null(params$output$Clasificacion)) {"# Clasification result"} `


`r if(!is.null(params$output$Clasificacion)& length(VariablesTarget)>1) {"## Correlation matrix"} `


```{r, eval=!is.null(params$output$Clasificacion) & length(VariablesTarget)>1, message=FALSE}

# paste("Minimun value of summary index suggets", Min, "clusters")
# kable(params$output$Clasificacion$ResultadosConglom)
# kable(params$output$Clasificacion$Indices)
kable(
  cor(params$output$Clasificacion$DatosConCongl[, VariablesTarget])
)

```

`r if(!is.null(params$output$Clasificacion)) {"## Clasification plot"} `

```{r}

ggplot(params$output$Clasificacion$DatosConCongl, 
       aes_string(x=Coordenadas[1], y=Coordenadas[2], colour=params$input$NumClust)) + 
  geom_point(size = 2)

print(params$output$corrVariables)
print(params$output$corrVariablesClust)

```


`r if(!is.null(params$output$Clasificacion)) {"## Descriptive statistics"} `


```{r, eval=!is.null(params$output$Clasificacion)}
## Zone Validation
# names(params$output)
kable(params$output$zoneValidationTables$Descriptivo)

```
`r if(!is.null(params$output$Clasificacion)) {"In parenthesis coefficient of variation"}`


`r if(!is.null(params$output$Clasificacion)) {"## Validation tables"} `

```{r, eval=!is.null(params$output$Clasificacion), results='asis', out.width="25%"}
myValidTables <- params$output$zoneValidationTables$Diferencias
for (i in seq_len(length(myValidTables))) {
  cat(paste('###', names(myValidTables)[i]))
  cat('\n\n')
  print(kable(myValidTables[[i]]))
  cat("\n\n\n")
  
}


```


```{r}
if (identical(rmarkdown::metadata$runtime, "shiny"))
  shiny::setProgress(1)  # set progress to 100%
```

